```{r data generation, echo = FALSE, results = "hide"}
library(exams)
## https://cerebralmastication.com/2020/07/27/using-python-sympy-in-a-python-code-chunk-in-rmarkdown/
## In console, I ran: reticulate::conda_install("r-reticulate","sympy")
library(reticulate)
min = 2
max = 7
use_condaenv(condaenv = "r-reticulate", required=TRUE)
deg = sample(min:max,1)
cf = c(sample(2:9,1)*sample(c(-1,1),1),sample(c(-9:9,rep(0,deg*4)),deg,T))
# make an R function for plotting.
s = paste("f=function(x){",cf[1],"*x^",deg,collapse="")
for(i in 2:length(cf)){
  if(cf[i]<0.1){
    s = paste(s,"-",abs(cf[i]),"*x^",deg-i+1,collapse="")
  } else if(cf[i]>0.1) {
    s = paste(s,"+",abs(cf[i]),"*x^",deg-i+1,collapse="")
  }
}
s = paste(s,"}")
eval(parse(text=s))
if(deg%%2==0 & cf[1]<0){
  sol = "1000"
  odev = "even"
  co1 = "negative"
  explain = "Thus the end behavior is down-down: when $x\\to -\\infty$ then $f(x)\\to -\\infty$ and when $x\\to \\infty$ then $f(x)\\to -\\infty$."
}
if(deg%%2==1 & cf[1]<0){
  sol = "0100"
  odev = "odd"
  co1 = "negative"
  explain = "Thus the end behavior is up-down: when $x\\to -\\infty$ then $f(x)\\to \\infty$ and when $x\\to \\infty$ then $f(x)\\to -\\infty$."
}
if(deg%%2==1 & cf[1]>0){
  sol = "0010"
  odev = "odd"
  co1 = "positive"
  explain = "Thus the end behavior is down-up: when $x\\to -\\infty$ then $f(x)\\to -\\infty$ and when $x\\to \\infty$ then $f(x)\\to \\infty$."
}
if(deg%%2==0 & cf[1]>0){
  sol = "0001"
  odev = "even"
  co1 = "positive"
  explain = "Thus the end behavior is up-up: when $x\\to -\\infty$ then $f(x)\\to \\infty$ and when $x\\to \\infty$ then $f(x)\\to \\infty$."
}
```


Question
========

Consider the polynomial function below.

```{python,results="asis",echo=F}
from sympy import symbols, Poly, latex
x = symbols("x")
po = Poly(list(map(int,r.cf)),x)
st = latex(po.as_expr())
```


$$f(x)=`r py$st`$$

Multiple choice: describe the end behavior.

* Down-down: when $x\to -\infty$ then $f(x)\to -\infty$ and when $x\to \infty$ then $f(x)\to -\infty$.
* Up-down: when $x\to -\infty$ then $f(x)\to \infty$ and when $x\to \infty$ then $f(x)\to -\infty$.
* Down-up: when $x\to -\infty$ then $f(x)\to -\infty$ and when $x\to \infty$ then $f(x)\to \infty$.
* Up-up: when $x\to -\infty$ then $f(x)\to \infty$ and when $x\to \infty$ then $f(x)\to \infty$.

Solution
========

The degree of the polynomial is `r deg`, which is `r odev`. The highest-degree term's coefficient is `r co1`. 

`r explain`



```{r,echo=F,fig.height=3,fig.width=3}
par(mar=c(0,0,0,0))
xx = seq(-100,100,length.out=1000)
yy = f(xx)
ymax = max(abs(yy))
plot(xx,f(xx),type="l",ylim=c(-ymax,ymax),axes=F,ann=F,lwd=3)
abline(h=0,col=rgb(0,0,0,0.5))
abline(v=0,col=rgb(0,0,0,0.5))
arrows(xx[2],yy[2],xx[1],yy[1],lwd=3)
arrows(xx[999],yy[999],xx[1000],yy[1000],lwd=3)
```


Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: end_behavior
extol: 0
exextra[numwidth,logical]: TRUE
