```{r data generation, echo = FALSE, results = "hide"}
## https://cerebralmastication.com/2020/07/27/using-python-sympy-in-a-python-code-chunk-in-rmarkdown/
## In console, I ran: reticulate::conda_install("r-reticulate","sympy")## In console, I ran: reticulate::conda_install("r-reticulate","matplotlib")
library(reticulate)
options(scipen = 100)

while(T){
  W = sample(seq(10,40,5),1)
  V = sample(seq(10,60,5),1)
  d = sample(seq(0.7,20,0.1),2) #kg/L = g/ml
  v = signif(sample(seq(0.01,1,0.01),2),1) #L
  w = signif(v*d,1) #kg
  ppg = 10^runif(2,0,3)
  p = signif(ppg*w,1)
  x = (W/w[2]-V/v[2])/(w[1]/w[2]-v[1]/v[2])
  y = (W/w[1]-V/v[1])/(w[2]/w[1]-v[2]/v[1])
  Pi = p[1]*x+p[2]*y
  xfullw = W/w[1]
  xfullv = V/v[1]
  yfullw = W/w[2]
  yfullv = V/v[2]
  xfull = min(xfullw,xfullv)
  yfull = min(yfullw,yfullv)
  xlim = max(xfullw,xfullv)
  ylim = max(yfullw,yfullv)
  Pxf = p[1]*xfull
  Pyf = p[2]*yfull
  Pmax = max(Pi,Pxf,Pyf)
  if(abs(w[2]*v[1]-w[1]*v[2])>0.01 & Pi==Pmax & Pxf<Pmax & Pyf<Pmax & x>1 & y>1 & w[1]!=w[2] & v[1]!=v[2] & p[1]!=p[2]){break}
}
```

Question
========

<!-- $$x = \frac{\frac{W}{w_2}-\frac{V}{v_2}}{\frac{w_1}{w_2}-\frac{v_1}{v_2}}$$ -->
<!-- $$y = \frac{\frac{W}{w_1}-\frac{V}{v_1}}{\frac{w_2}{w_1}-\frac{v_2}{v_1}}$$ -->
<!-- $$v_1x+v_2y\le V$$ -->
<!-- $$w_1x+w_2y\le W $$ -->
<!-- To determine intersection... -->
<!-- $$y = -\frac{v_1}{v_2}x+\frac{V}{v_2} $$ -->
<!-- $$y = -\frac{w_1}{w_2}x+\frac{W}{w_2} $$ -->
<!-- $$ -\frac{c_1}{c_2}x+\frac{C}{c_2} = -\frac{d_1}{d_2}x+\frac{D}{d_2}  $$ -->
<!-- $$x = \frac{\frac{W}{w_2}-\frac{V}{v_2}}{\frac{w_1}{w_2}-\frac{v_1}{v_2}}$$ -->
<!-- $$y = \frac{\frac{W}{w_1}-\frac{V}{v_1}}{\frac{w_2}{w_1}-\frac{v_2}{v_1}}$$ -->
<!-- diamond density: 3.51 g/cm -->
<!-- diamond price/carat = 1200-68000 -->
<!-- price/gram = 6000 - 340000 -->

<!-- gold density: 19.3 g/cm3 -->
<!-- gold price/gram: $61/g -->

<!-- platinum density: 21.45 g/cm3 -->
<!-- platinum price: $35/g -->

<!-- silver density: 10.49 g/cm3 -->
<!-- silver price: $0.78/g -->

<!-- density: 0.5 g/cm - 20 g/cm -->
<!-- price: 1 USD/g - 10,000 USD/g -->


A thief is filling her backpack with two types of valuable substances. She can carry up to `r W` kg, and her backpack can fit up to `r V` liters. 

Each bag of $X$ has a weight of `r w[1]` kg, volume of `r v[1]` L, and value of `r p[1]` thousand USD.

Each bag of $Y$ has a weight of `r w[2]` kg, volume of `r v[2]` L, and value of `r p[2]` thousand USD.

There is no requirement to take full bags, so the thief can opt for a fraction of a bag.

How many bags of each should the thief take to maximize her profit?


Solution
========

The thief should take `r round(x,2)` bags of $X$ and `r round(y,2)` bags of $Y$. We can use linear programming to see this.

We write a weight inequality.
$$`r w[1]`x+`r w[2]`y \le `r W`$$
We write a volume inequality.
$$`r v[1]`x+`r v[2]`y \le `r V`$$
We graph the two inequalities, shading the feasible region.
```{r,echo=F}
xx = seq(0,xlim,0.01)
x2 = seq(0,xfull,0.01)
plot(xx,yfull-yfull/xlim*xx,type="l",xlim=c(0,xfull*1.2),ylim=c(0,yfull*1.2),lwd=3,ylab="bags of Y",xlab="bags of X")
lines(x2,ylim-ylim/xfull*x2,lwd=3)
polygon(c(0,0,x,xfull,0),c(0,yfull,y,0,0),col=rgb(0.5,0.5,0.5,0.5))
points(c(0,x,xfull),c(yfull,y,0))
```

There are three vertices of interest.
$$(0,`r round(yfull,2)`) $$
$$(`r round(x,2)`,`r round(y,2)`) $$
$$(`r round(xfull,2)`,0)$$

We write a profit function (the objective function).
$$P(x,y) = `r p[1]`x+`r p[2]`y $$

We determine the profits.
$$P(0,`r round(yfull,2)`)=`r round(p[2]*yfull,2)` $$
$$P(`r round(x,2)`,`r round(y,2)`)=`r round(p[1]*x+p[2]*y,2)` $$
$$P(`r round(xfull,2)`,0)=`r round(p[1]*xfull,2)` $$
Thus, the thief should take `r round(x,2)` bags of $X$ and `r round(y,2)` bags of $Y$.

<!-- Note: we could also draw isoprofit lines, seeing that an isoprofit line has a slope between the slopes of the weight and volume constraints. -->


Meta-information
============
extype: string
exsolution: nil
exname: linear_programming_thief
