```{r data generation, echo = FALSE, results = "hide"}
library(pracma)
## https://cerebralmastication.com/2020/07/27/using-python-sympy-in-a-python-code-chunk-in-rmarkdown/
## In console, I ran: reticulate::conda_install("r-reticulate","sympy")## In console, I ran: reticulate::conda_install("r-reticulate","matplotlib")
library(reticulate)

while(T){
a1 = sample(1:20,9,T)*sample(c(-1,1),9,T)
a = matrix(a1,ncol=3,byrow=T)
x = sample(1:10,3)*sample(c(-1,1),3,T)
b = a%*%x
ex1 = paste0('',a[1,1],'*x+(',a[1,2],')*y+(',a[1,3],')*z')
ex2 = paste0('',a[2,1],'*x+(',a[2,2],')*y+(',a[2,3],')*z')
ex3 = paste0('',a[3,1],'*x+(',a[3,2],')*y+(',a[3,3],')*z')
sol = rref(cbind(a,b))
if(sol[1,1]==0 || sol[2,2]==0 || sol[3,3]==0){break}
}
```

```{python,echo=F}
import sympy as sp
x = sp.symbols("x")
y = sp.symbols("y")
z = sp.symbols("z")
ex1 = sp.parse_expr(r.ex1)
ex2 = sp.parse_expr(r.ex2)
ex3 = sp.parse_expr(r.ex3)
# eq1 = sp.Eq(ex1,int(r.b[0][0]))
# eq2 = sp.Eq(ex2,int(r.b[1][0]))
lex1 = sp.latex(ex1)
lex2 = sp.latex(ex2)
lex3 = sp.latex(ex3)
A = list(map(int,r.a1))
A = sp.Matrix(3,3,A)
B = list(map(int,r.b))
A = A.col_insert(3,sp.Matrix(B))
sol = A.rref()
```

Question
========

Solve the following system.

$$\begin{align}
`r py$lex1`&=`r b[1]`\\
`r py$lex2`&=`r b[2]`\\
`r py$lex3`&=`r b[3]`
\end{align}$$


Solution
========

The system is undetermined. There are infinite solutions. This might be because two planes are equivalent, or because all three planes meet in a line, or because all three planes are equivalent.

Here is one solution:

$$\begin{align}
x&=`r x[1]`\\
y&=`r x[2]`\\
z&=`r x[3]`
\end{align}$$


Here is the reduced row echelon form:

```{r,echo=F}
print(sol)
```

And, here are the planes graphed (unfortunately the graphing method has trouble deciding which plane in in front).

```{python, echo=F}
import matplotlib
from sympy.plotting import plot3d
p1 = sp.solve(ex1-B[0],z)[0]
p2 = sp.solve(ex2-B[1],z)[0]
p3 = sp.solve(ex3-B[2],z)[0]
plt = plot3d(p1,p2,p3,(x,-10,10),(y,-10,10),nb_of_points_x=3,nb_of_points_y=3)
```


Meta-information
============
extype: cloze
exsolution: `r x[1]`|`r x[2]`|`r x[3]`
exclozetype: num|num|num
exname: linear_system_2_standard
extol: 0
exextra[numwidth,numeric]: 8

